%-------------------------
% Resume in Latex
% Author : James Xie
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/jamesjingxie/}{\Large James Xie}} & Email : \href{mailto:jxie418@gmail.com}{jxie418@gmail.com}\\
  \href{https://github.com/jxie418/}{https://github.com/jxie418} & Mobile : +1312-379-9838 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DePaul University}{Chicago, IL}
      {Master of Computer Science;  GPA: 3.9/4.0}{Sep. 2008 -- July. 2010}
    \resumeSubheading
      {Beihang University}{Beijing, China}
      {Master of Computer Science;  GPA: 3.8/4.0 }{Sep. 2004 -- May. 2007}
  \resumeSubHeadingListEnd


%-----------SUMMARY OF QUALIFICATIONS-----------------
\section{SUMMARY OF QUALIFICATIONS}
  \resumeSubHeadingListStart
    \resumeSubItem{Total years}
    {14+ years of overall experience as software developer in design, development, deploying and large scale supporting for large distributed systems using Java, Scala and Kotlin.}
    \resumeSubItem{Big Data}
    {6+ years Big Data experience on Spark, Kafka, Hadoop, HDFS, Hive, Zookeeper, Cassandra, Kubernetes, GCP, AWS. 6+ years experience in custom ETL design, implementation and maintenance.}
    \resumeSubItem{Cloud}
    {6+ years experience on Amazon S3, EC2, GCP. 6+ years on NoSql Database like Cassandra and MangoDB}
    \resumeSubItem{No SQL}
    {Good understanding of NoSQL Data bases and hands on work experience in writing applications on No SQL data bases like Cassandra and Mongo DB.}   
    \resumeSubItem{Generic}
    {Strong software development, problem solving skill, debugging skills and  good learning ability and nice personality and strong knowledge of OO programming techniques, Modular design skills.Good understanding of agile development and software development lifecycle and strong problem solving and troubleshooting.}
    \resumeSubItem{Generic}
    {Strong experience in core Java, Scala, SQL, PL/SQL and Restful web services and microservices.}
    \resumeSubItem{Generic}
    {Having good knowledge in Benchmarking & Performance Tuning of cluster.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java/J2EE, Scala, Kotlin, Python, Javascript, Shell Scripts, C++/C, SQL, PL/SQL, UML, JSP, HTML}
      \hfill
      \textbf{Technologies}{: GCP, Kubernates, HDFS, Map Reduce YARN, Spark, AWS, EC2, S3, Play, Kafka, Cassandra, Oracle, Mysql, GCE, Spring Boot, Spring MVC,  Hibernate, JPA, Servlets, JDBC, JMS, Git}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dexcom}{San Diego, CA}
      {Sr Staff Data Engineer}{May 2016 - Present}
      \resumeItemListStart
        \resumeItem{Streaming Pipeline}
          {Design and implemented the scalable big data platform and streaming data pipelines using Scala, Spark, Kafka and Cassandra. Created Bamboo build plan for the daily build and release build. Created deploy scripts to auto deploy our data pipeline on Kubernetes cluster. Using Vault to store the PKI certificate and database username and passward.}
        \resumeItem{New Share Backend API}
          {Desing and implemented new Scalable backend RESTful APIs using Kotlin, Spring Boot, Mysql Cluster, Kafka, Cassandra.}
        \resumeItem{Global Configuration Service API}
          {Designed and implemented global configuration service api for Dexcom one app application. It provides generic configuration values based on user profile information. It used Scala, Play Framework, Cassandra, Bamboo.}
        \resumeItem{Data Ingestion Pipeline}
          {Design and implemented very efficient and reliable streaming pipeline using spark kafka streaming api ingesting the live uploaded CGM data into Casandra database. Created alerts and monitoring based on spark job JMX metrics.}
        \resumeItem{Partner Integration Pipeline}
          {Design and implemented partner integtation pipeline using Apache Beam and deployed at GCP as Dataflow job. It streamed the GCM data of participates from partners to pub/sub topic which belong to the partner. It used Scala, Beam, Scio, Dataflow, GCP.}
        \resumeItem{Reconciliation and Recovery Framework}
          {Design and implemented a reconciliation and recovery Framework for our internal pipelines. It is highly resuable Framework to ensue that he message from incomeing topic is processed and send to right destination}
        \resumeItem{Discovery Pipeline}
          {Design and implemented Discovery pipeline for Dexcom partner. It is for panter blind test user case and delivery the message to partner Pub/Sub topic.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {AudexExplore}{San Diego, CA}
      {Senior Software Engineer}{Dec 2012 - May 2016}
      \resumeItemListStart
        \resumeItem{Compliance Check Engine}
          {Developed a new compliance check engine for car estimates. It evaluates the compliance
rules for all the estimates and generates compliance reports for the customers. Used Java, JXLS, J2EE, Spring, Hibernate, GIT, Click Servlet Framework, Velocity,
JUnit, Easy Mock, JavaScript, JQuery, Ajax, Tomcat, Oracle database for this project.} 
        \resumeItem{Digital Garage Backend}
          {Developed Restful API backend for digital grarage mobile apps which using Java, Sprint boot, Hibernate, Maven 3, GIT Mysql, AWS, EC2, S3, Swagger UI, Power Mock Junit.}
        \resumeItem{AudaMobile}
          {Developed mobile apps for quick estimate for insurance companies.}
         \resumeItem{Claims Dashboards}
          {Design and implemented Claims management Dashboards front end and backend. The front used Angular js and backed used Java, J2EE, Spring Boot, Spring MVC.}    
      \resumeItemListEnd

    \resumeSubheading
      {VinaKom Communication}{Schaumburg, IL}
      {Software Engineer}{Sep. 2011 and Dec. 2012}
      \resumeItemListStart
        \resumeItem{IP Phone System}
          {Created IP phone system configuration GUI and the PBX system.}
%        \resumeItem{QuantDesk}
%         {Python backend for a web application used by hedge fund managers for portfolio management.}
      \resumeItemListEnd

    \resumeSubheading
      {Great Arc Technologies}{Chicago, IL}
      {Software Engineer}{July 2010 - Sep 2011}
      \resumeItemListStart
        \resumeItem{Mobile application for Forest Preserve District of Cook Country}
          {This project developed and implemented a smart phone application for iPhone and BlackBerry devices, which gives users interactive access to Forest Preserve maps, locations, activities, photos, and events. The application includes a user-friendly search function for locating particular areas of interest.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
